\documentclass{resume}
\usepackage[T1,T2A]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{cmap}
\usepackage[english]{babel}
\usepackage[left=0.4in,top=0.4in,right=0.4in,bottom=0.4in]{geometry}
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}

\name{Maksim Kiryakin}
\address{+7 (916) 344-6061 \\ Russia, Moscow}
\address{\href{mailto:makxim.kiryakin@gmail.com}{makxim.kiryakin@gmail.com} \\
	\href{https://github.com/MaximKiryakin}{github.com/MaximKiryakin} \\
	\href{https://t.me/Maxim_Kiryakin}{@Maxim\_Kiryakin} \\
}%

\begin{document}

	\begin{rSection}{Summary}
		\textbf{Data Scientist with 2+ years of experience} in classical machine learning, econometrics, and mathematical programming.
		Specializing in scalable ML solutions and financial analytics. Delivered clustering pipeline for 120M+ users and deployed NPV models to production, driving data-driven decision-making. Proficient in Python (PySpark, Pandas), SQL, and end-to-end ML pipelines.
	\end{rSection}

	\begin{rSection}{Education}
		\textbf{Lomonosov Moscow State University (Master's degree)} \hfill {September 2024 - Present}\\
		Faculty of Computational Mathematics and Cybernetics (\textit{GPA:} 4.4/5).\\
		\textbf{Lomonosov Moscow State University (Bachelor's degree)} \hfill {September 2020 - June 2024}\\
		Faculty of Computational Mathematics and Cybernetics (\textit{GPA:} 4.3/5).
	\end{rSection}

	\begin{rSection}{Work Experience}
		\textbf{Sber} \hfill {May 2024 - Present}\\
		Data Scientist, Investment Expertise Directorate (Finance Division) \\
		\vspace{-1.25em}
		\begin{itemize}
			\itemsep -3pt {}
			\item Architected and productionized a scalable customer clustering pipeline for 120M+ profiles using PySpark.
			\item Led R\&D to define, implement a new bank-wide metric, including statistical evaluation and experiments.
			\item Developed, validated, and deployed ML and econometric model to estimate product NPV; integrated them with
			data pipelines and established monitoring, maintenance, and business-acceptance procedures to ensure robustness and interpretability.
			\item Stack: Python (PySpark, Pandas, Scikit-learn), SQL, Hive, Git, Excel.
		\end{itemize}

		\textbf{Sber} \hfill {August 2023 - March 2024}\\
		Intern, Balance Sheet Structure Department (Finance Division) \\
		\vspace{-1.25em}
		\begin{itemize}
			\itemsep -3pt {}
			\item Refactored and modularized legacy Python prototypes, added unit tests and documentation to improve maintainability and accelerate onboarding.
			\item Integrated a pre-trained ML model into the production pipeline, improving target prediction quality by 30\% on validation data and ensuring reproducible inference.
			\item Optimized the main computation (profiling-driven algorithmic refactor and vectorization), achieving a 3× speedup and reduced memory footprint.
			\item Developed automated ETL workflows to extract, validate and preprocess large datasets from HDFS using PySpark/Python, with logging and error handling for reliable runs.
			\item Stack: Python (PySpark, Pandas, Scikit-learn), SQL, Hive, Excel.
		\end{itemize}
	\end{rSection}

	\begin{rSection}{Skills}
		\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
			Programming: & Python, SQL, C/C++ \\
			Data \& ML: & PySpark, Pandas, NumPy, SciPy, Scikit-learn, PyTorch, SQL, Hive \\
			Tools: & Git, Excel \\
			Concepts: & Feature engineering, clustering, time-series, econometrics, model deployment
		\end{tabular}\\
	\end{rSection}

	\begin{rSection}{Professional Development}
		\begin{itemize}
			\item \textit{Apache Spark for Data Analysis Tasks} — New Professions Lab
			\hfill \href{https://github.com/MaximKiryakin/My-Resume/blob/master/english_version/Sertificate1.png}{Certificate (with honors)}

			\item \textit{Methods of Data Analysis and Machine Learning} — Sber University
			\hfill \href{https://github.com/MaximKiryakin/My-Resume/blob/master/english_version/Sertificate2.png}{Certificate (with honors)}

			\item \textit{Mathematical Models in Investment Banks} — Deutsche Bank Technology Center
		\end{itemize}
	\end{rSection}

\end{document}